Cover Times of Random Walks

### 2019-09-01 paper.tex
integrate Bill's feedback

Let $C_{i,j}=C_{j,i}$ be a non-negative weight assinged to the edge
between vertices $i$ and $j$.
We will mostly consider unweighted graphs,
meaning $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.

@@

Let $T_{j}$ be the number of steps until the first visit to $j$
after time time $t=0$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
\end{align}
Let $\E_i[T_j] = \E[T_j | X_0 = i]$.
This is the expected time of the first visit to $j$ given
that the random walk started in vertex $i$.
Then $\E_j[T_j]$ is the return time to $j$
since $t$ is strictly positive.
Now define the hitting time $\hit$ for the graph
be the maximum expected time between two vertices on $G$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Let the cover time variable $\cov$ be the first time all vertices have been
visited by the random walk $(X_t)$.
Formally, $\cov$ is the minimum time that for all $i \in V(G)$
there exists $t \leq \cov$ such that $X_t = i$.
We define the cover time as the expected value of $\cov$ from
the worst initial vertex.
Formally,
\begin{align}
\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
\end{align}

@@

So that the reader may more easily distinguish between
vertices, consider $x$ and $y$ in $V(G)$.
Recall that $C_{x,y}$ is the weight of the edge
between vertices $x$ and $y$, $C_x$ is the sum
of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
that we go from $x$ to $y$ is $C_{x,y}/C_x$.
For the rest of this section, we will call $C_{x,y}$
the conductance between $x$ and $y$.
Define the resistance $R_{x,y}$ between $x$ and $y$
as $1/ C_{x,y}$.
(We will soon justify the electrical network interpretation of
a random walk using Ohm's Law.)

We now consider the distribution of the random
walk on the vertices of our graph.
Define the proportion $\pi_x$ of time we spend in $x$
as $C_x/C$ where $C=\sum_y C_y$.

We verify that $\pi$ is the stationary distribution
of $(X_t)$.
To begin,
\begin{align}
C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
\end{align}
Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
(So $\pi$ satisfies detailed balance.)
Summing over $x$,
\begin{align}
\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
\end{align}
In the language of Markov Chains,
$\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
It follows that $\pi$ is the stationary distribution of $(X_t)$.
The takeaway for the reader unfamiliar with Markov Chains is that
$\pi_y$ is indeed the long term proportion of time spent in vertex $y$.

We now introduce voltage, current, and effective resistance.
Consider $a$ and $b$ in $V(G)$.
Set the voltage to be 1 at $a$ and 0 at $b$.
We may think of voltage as the probability we get to $a$ before $b$:
$v_a$ the probability we get to $a$ before $b$ from $a$
is 1 and $v_b$ the probability we get to $a$ before $b$ from $b$ is 0.
The voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
is determined by the boundary values (at $a$ and $b$).

By Ohm's Law, the current between two vertices is the product of the
difference in their voltages and the conductance of their edge.
We may think of current as the net number of movements through an edge.
Kirchoff's Current Law says that the sum of current on any vertex is 0.
Probabilistically: every time we enter a vertex we must also leave it.
Using Kirchoff's Current Law and the definition of current,
we justify the probabilistic interpretation of voltage
\begin{align}
\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
\end{align}
We can verify that $v_x = \sum_y \pr_{x,y} v_y$
using total probability on the likelihood of reaching $a$ before $b$ from $x$.

@@

We begin in \cref{sec:small_example}.
(\cref{sec:structured_graphs} primarily relies on \cite{BH94}.)
We see that while in principle it is always possible to exactly 
calculate the cover time
of graph, it is in general very difficult to do so.
For the remainder of this section, we investigate
structured graphs for which exact cover time analysis is tractable:
the complete graph, line graphs, and simple cycles.

@@

Up until \cref{sec:dist}, we only consider expected cover time.
We now delve into the distribution of the cover time on a complete graph with self-edges.
We draw on \cite{Du11} and find that the cover time variable approaches a Poisson
distribution.
In \cref{sec:birthday}, we apply \cref{sec:complete_dist} to the birthday problem.
(The R code for our computations and \cref{fig:birthday} can be found in \cref{app:birthday}.)

@@

\subsection{Small Example}\label{sec:small_example}
In general, it is always possible to find the exact cover time
of a graph using first step analysis.
We demonstrate the strategy on a small graph suggested by \cite{BH94}.

@@

For a graph with $n$ vertices, there are $n$ possible choices for the current
vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
for each one.
Of course, some cases are inaccessible by a random walk.
But even on \cref{fig:example} where we exploit symmetry,
there are almost a prohibitive number.
It is easy to see that the number of cases 
grows exponentially with the number of vertices.
\begin{comment}
\begin{figure}[ht]
	\centering
		\begin{tikzpicture} [
            > = stealth, % arrow head style
            shorten > = 1pt, % don't touch arrow head to node
            %auto,
            node distance = 3cm, % distance between nodes
            semithick % line style
        ]

@@

\subsection{Complete Graph}\label{sec:complete}
We call the graph with an edge between each pair of vertices the
complete graph.
Note that a complete graph with $n$ vertices has ${n \choose 2}$ edges.

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i+1)/(n-1)$.
This is because there are $n-i+1$ unvisited 
vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (n-1)/(n-i+1)$.
Since we start at a vertex, $\E[X_i]=0$.
Then
\begin{align}
\tcov&=   0+\sum_{i=2}^{n} \frac{n-1}{n-i+1} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
\end{align}

@@

Another more subtle application of the cover time on a complete graph
is the cover time on an $n$-star.

@@

An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
edge to the center.
A random walk begins at the central vertex and moves with uniform probability to
one of the $n-1$ adjacent vertices.
Whereas in the complete graph and coupon collecting problems we 
visited a (possibly) new vertex in one step,
a random walk on the $n$-star visits a (possibly) new vertex
in two steps: one step to each leaf and one step back.
We apply our approach to the complete graph and conclude that

@@

To solve the telescoping equations, observe that the walk is symmetric:
we could flip the walk over the vertical axis without changing $e_i$.
This makes sense because our intuition tells us that the only 
identifying feature of $i$ is its respective distances to the endpoints.
The logical conclusion is that $e_i=e_{N-i}$.
In particular, we have already seen that $e_0=e_N=0$ and it
naturally follows that $e_1=e_{N_1}$.
We use these observations to find $e_1$:

@@

\cref{thm:line} follows from \cref{eq:line} and the observation that any
line graph can be shifted so that the left endpoint
is at $0$ and the right endpoint is at $N$.

@@

We write
\begin{align}
\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \cdots + \E_{i}[T_{i+1}] + \cdots + \E_{N-1}[T_N]. \nonumber
\end{align}

where $\E_{i}[T_{i+1}]$ is the expected time from state $i$ to $i+1$.
Since there is only one edge incident to 0, we always move from 0 to 1.
From state $i\neq0$, we take one step in each direction with equal probability.
In half the cases, we have arrived at $i+1$.
In the other half of cases, we are in $i-1$.
It will take us $\E_{i-1}[T_i]$ steps back to $i$ and then another
$\E_i[T_{i+1}]$ steps to $i+1$.
Formally,
\begin{align}
\E_{i}[T_{i+1}] &= 1 + \frac{1}{2}(\E_{i-1}[T_i]+\E_i[T_{i+1}]) +\frac{1}{2}0 \nonumber \\
 &= 2 + \E_{i-1}[T_{i}]. \nonumber
\end{align}

@@

\subsection{Commute Time Identity} \label{sec:commute}
\cite{DS84} We use the electrical network analysis in \cref{sec:electric} to 
prove the commute time identity so we may use it to help us bound
cover times.

@@

Our goal is to bound the cover time in terms of the hitting time.
Consider the first term of the sum.
Recall that the hitting time $\hit$ is the maximum
expected time from any vertex to any other.
It follows that for any choice of $\sigma_1$,
the expected time from $n$ to $\sigma_1$ is less than or equal to $\hit$.
Formally for $s$ an arbitrary state such that $1\leq s \leq n-1$,
$\E_n[T_1] = \E_n[T_s] \leq \hit$.

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale = 2]
	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
	    \node[vertex] (0) at (0,3) {};
	    \node[vertex] (1) at (1,2) {};
	    \node[vertex] (2) at (-1,2) {};
	    \node[vertex] (3) at (1.5,1) {};
	    \node[vertex] (4) at (.5,1) {};
	    \node[vertex] (5) at (-.5,1) {};
	    \node[vertex] (6) at (-1.5,1) {};
	    \node[vertex] (7) at (1.75,0) {};
	    \node[vertex] (8) at (1.25,0) {};
	    \node[vertex] (9) at (.75,0) {};
	    \node[vertex] (10) at (.25,0) {};
	    \node[vertex] (11) at (-.25,0) {};
	    \node[vertex] (12) at (-.75,0) {};
	    \node[vertex] (13) at (-1.25,0) {};
	    \node[vertex] (14) at (-1.75,0) {};
	    \draw[edge] (1) -- (0);
	    \draw[edge] (2) -- (0);
	    \draw[edge] (1) -- (3);
	    \draw[edge] (4) -- (1);
	    \draw[edge] (2) -- (5);
	    \draw[edge] (6) -- (2);
	    \draw[edge] (3) -- (7);
	    \draw[edge] (3) -- (8);
	    \draw[edge] (4) -- (9);
	    \draw[edge] (4) -- (10);
	    \draw[edge] (5) -- (11);
	    \draw[edge] (5) -- (12);
	    \draw[edge] (6) -- (13);
	    \draw[edge] (6) -- (14);
	\end{tikzpicture}
	\caption{A binary tree with $k=3$ and $n=15$.}\label{fig:binary}
\end{figure}

\cite{LP17}
Consider an unweighted binary tree as in \cref{fig:binary} with a single root $\rho$.
A vertex has two children if it is distance less than $k$
from the root and no children if it is a leaf (distance $k$ from the root).
There are $n = 1 + 2 + 4 + \cdots + 2^k = 2^{k+1} - 1$ vertices.

By \cref{eqn:commute}, the commute time between the root and a leaf $a$ is
\begin{align}
C R_{\rho, a} = 2 (n-1) k \nonumber.
\end{align}
Note that resistance adds in series so 
effective resistance is just the sum of the resistances along a path.
Then $\Rxy = i$ where $i$
is the length of the single path between $x$ and $y$.

@@

\subsection{Spanning Tree Argument}\label{sec:spanning}
\cite{AF14}
We introduce the concept of a spanning tree to create
another upper bound for the cover time of a random walk.

@@

A spanning tree $\T$ is a subset of a graph with all vertices 
in $V(G)$ connected by the minimum number of edges in $E(G)$.
\cref{fig:span} is an example where the bold edges indicate the edges in $E(\T)$
and the light edges indicate the edges in $E(G)$ but not $E(\T)$.
For the connected graphs we consider, the minimum number of edges
needed to connect all vertices is $n-1$.
Formally, $V(\T) = V(G)$ and $E(\T) \subseteq E(G)$
such that $|E(\T)| = n-1$ and $\T$ is connected.

@@

We compute the variance of $N_n$ by finding $\E[N_n^2]$ and $\E[N_n]^2$.
Let $\I_m$ be the indicator random variable for event $A_m$.
That is, $\I_m = 1$ if vertex $m$ is unvisited 0 otherwise.
We first find $\E[N_n^2]$
\begin{align}
\E[N_n^2] &= \E \left[ \left(\sum_{m=1}^n \I_m \right) ^2 \right] =
\E \left[ \sum_{m=1}^n \sum_{k=1}^n \I_m \I_k \right] =
\sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m). \nonumber
\end{align}
The second equality holds since we distribute terms.
The third equality holds since the mean of an indicator for event $A_m$
is the probability of $A_m$ and both events must occur for
us to have a nonzero term.
Then we find $\E[N_n]^2$
\begin{align}
\E[N_n]^2 &= \E \left[ \left(\sum_{m=1}^n \I_m \right)
\left( \sum_{k=1}^n \I_k \right) \right] =
\sum_{1 \leq k, m \leq n} \pr(A_k) \pr(A_m).
\nonumber
\end{align}

Putting both together, we find the variance
\begin{align}
\Var[N_n] &= \E[N_n^2] - \E[N_n]^2 \nonumber \\
&= \sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m) - P(A_k)P(A_m) \nonumber \\
&= n(n-1) \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} + 
n \{ \pr(A_k \cap A_m) - P(A_k)P(A_m) \} \nonumber \\
&= n(n-1) \{ (1-2/n)^r - (1-1/n)^{2r} \} + 
n \{ (1-1/n)^r  - (1-1/n)^{2r} \}. \nonumber
\end{align}
where $k\neq m$ in the first term and $k=m$ in the second.

@@

Thus we conclude that $N_n/n \rightarrow e^{-c}$.

The Poisson approximation of the binomial implies that if $n \rightarrow \infty$
and $r/n \rightarrow c$, then the number of visits to each vertex will approach
a Poisson distribution with mean $c$.
We can use this to intuite our latest result: the proportion of visits to each vertex
approaches $e^{-c}$.

@@

\begin{proof}
Observe that the probability that there are $k$ unvisited vertices is
\begin{align}
(1-k/n)^r \nonumber.
\end{align}

@@

If we consider the locations of the unvisited vertices,
\begin{align}
p_m(r,n) = {n \choose m} \left(1-\frac{m}{n}\right)^r p_0(r, n-m). \nonumber
\end{align}

@@

We now turn to the more tricky lower bound.
Notice that ${n \choose m} \geq (n-m)^m / m!$
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r
&\geq \left(1-\frac{m}{n}\right)^r \frac{(n-m)^m}{m!}
\left( \frac{n^m}{n^m} \right) \nonumber\\
&\geq n^m (1 - \frac{m}{n})^r (1- \frac{m}{n})^m  \frac{1}{m!}. \nonumber
\end{align}

As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$
and $1/m!$ is constant.
We use the Taylor series of $\log(1-t)$ for $0 \leq t \leq 1/2$
to bound the rest,
\begin{align}
\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \cdots \nonumber\\
&\geq -t -t^2/2(1 + 1/2 + 1/4 + \cdots) = -t - t^2 \nonumber
\end{align}
and so we have
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
& \geq m \log n - r\frac{m}{n} - r\left(\frac{m}{n}\right)^2. \nonumber
\end{align}

>>>>

Let $C_{i,j}=C_{j,i}$ be a non-negative weight assigned to the edge
between vertices $i$ and $j$.
We will mostly consider unweighted graphs,
meaning $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.

@@

Let $T_{j}$ be the number of steps until the first visit to $j$
after time time $t=0$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
\end{align}
Let $\E_i[T_j] = \E[T_j | X_0 = i]$.
This is the expected time of the first visit to $j$ given
that the random walk started in vertex $i$.
Then $\E_j[T_j]$ is the return time to $j$
since $t$ is strictly positive.
Now define the hitting time $\hit$ for the graph
be the maximum expected time between two vertices on $G$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Let the cover time random variable $\cov$ be the first time all vertices have been
visited by the random walk $(X_t)$.
Formally, $\cov$ is the minimum time that for all $i \in V(G)$
there exists $t \leq \cov$ such that $X_t = i$.
We define the cover time as the expected value of $\cov$ from
the worst initial vertex.
Formally,
\begin{align}
\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
\end{align}

@@

So that the reader may more easily distinguish between
vertices, consider $x$ and $y$ in $V(G)$.
Recall that $C_{x,y}$ is the weight of the edge
between vertices $x$ and $y$, $C_x$ is the sum
of all $C_{x,y}$ where $x$ and $y$ share an edge,
and the probability $\pr_{x,y}$
that we go from $x$ to $y$ is $C_{x,y}/C_x$.
For the rest of this section, we will call $C_{x,y}$
the conductance between $x$ and $y$.
Define the resistance $R_{x,y}$ between $x$ and $y$
as $1/ C_{x,y}$.
(We will soon justify the electrical network interpretation of
a random walk using Ohm's Law.)

We now consider the distribution of the random
walk on the vertices of our graph.
Define $\pi_x$ as $C_x/C$ where $C=\sum_y C_y$.
We will show that $\pi$, the vector of $\pi_i$ where $i$
runs over all vertices, is the stationary distribution of the random walk.
Then $\pi_x$ must be the long term proportion of time spent in vertex $x$.
We first use our definitions to show that $\pi$ satisfies detailed balance,
\begin{align}
C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
\end{align}
Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$,
or detailed balance.
We next use detailed balance to show that $\pi$ is the stationary distribution.
Summing over $x$,
\begin{align}
\sum_x \pi_x \pr_{x,y} = \sum_x \pi_y \pr_{y,x} = \pi_y \sum_x \pr_{y,x}
= \pi_y . \nonumber
\end{align}
(We get the last equality because we know that when leaving vertex $y$
the random walk goes with probability 1 to some vertex $x$.)
We rely on \cite{Ka14} to show that 
$\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities
and how it follows that $\pi$ is the stationary distribution of the random walk.
Then $\pi_x$ is indeed the long term proportion of time spent in vertex $x$.

We now introduce voltage, current, and effective resistance.
Consider arbitrary $a$ and $b$ in $V(G)$.
This is equivalent to setting the voltage to be 1 at $a$ and 0 at $b$.
We may think of voltage $v_x$ as the probability starting
from $a$ we get to $x$ before $b$.
(We have not proved this yet but we will by the end of this subsection.)
With this interpretation
it makes sense that $v_a$, the probability we get to $a$ before $b$, is 1
(we are already at $a$) 
and $v_b$, the probability we get to $b$ before $a$, is 0
(we are again already in $a$).
We do not prove this but
the voltage at every vertex $x$ in  $V(G) \textbackslash \{a,b\}$
is determined by the boundary values at $a$ and $b$.

By Ohm's Law, the current between two vertices is the product of the
difference in their voltages and the conductance of their edge.
We may think of current as the net number of movements through an edge.
Kirchoff's Current Law says that the sum of current on any vertex is 0.
Probabilistically, every time we enter a vertex we must also leave it.
Using Kirchoff's Current Law and the definition of current,
we justify the probabilistic interpretation of voltage as follows
\begin{align}
\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
\end{align}
It follows that $v_x = \sum_y \pr_{x,y} v_y$
using total probability on the likelihood of reaching $a$ before $b$ from $x$.

@@

\cref{sec:structured_graphs} primarily relies on \cite{BH94}.
We see that while in principle it is always possible to exactly 
calculate the cover time
of graph, it is in general very difficult to do so.
For the remainder of this section, we investigate
structured graphs for which exact cover time analysis is tractable:
the complete graph, line graphs, and simple cycles.

@@

Up until \cref{sec:dist}, we only consider expected cover time.
We now delve into the distribution of the cover time on a complete graph with self-edges.
We draw on \cite{Du11} and find that the cover time random variable
approaches a Poisson distribution as the number of vertices goes to infinity.
In \cref{sec:birthday}, we apply \cref{sec:complete_dist} to the birthday problem.
(The R code for our computations and \cref{fig:birthday} can be found in \cref{app:birthday}.)

@@

\subsection{Small Example}\label{sec:small_example}
In principle, it is always possible to find the exact cover time
of a graph using first step analysis.
We demonstrate the strategy on a small graph suggested by \cite{BH94}.

@@

For a graph with $n$ vertices, there are $n$ possible choices for the current
vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
for each other one.
Of course, some cases are inaccessible by a random walk.
But even on \cref{fig:example} where we exploit symmetry,
there are almost a prohibitive number.
It is easy to see that the number of cases 
grows exponentially with the number of vertices.
\begin{comment}
\begin{figure}[ht]
	\centering
		\begin{tikzpicture} [
            > = stealth, % arrow head style
            shorten > = 1pt, % don't touch arrow head to node
            %auto,
            node distance = 3cm, % distance between nodes
            semithick % line style
        ]

@@

\subsection{Complete Graph}\label{sec:complete}
We call the graph with an edge between each pair of vertices the
complete graph.
Note that a complete graph with $n$ vertices has ${n \choose 2}$ edges.
(We exclude self-edges.)

@@

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i+1)/(n-1)$.
This is because there are $n-i+1$ unvisited 
vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (n-1)/(n-i+1)$.
Since we start at a vertex, $\E[X_1]=0$.
Then
\begin{align}
\tcov&=   0+\sum_{i=2}^{n} \frac{n-1}{n-i+1} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+\cdots+1\right). \nonumber
\end{align}

@@

@@

Another more subtle application of the cover time on a complete graph
is the cover time on an $n$-star.
An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
edge to the center.
A random walk begins at the central vertex and moves with uniform probability to
one of the $n-1$ adjacent vertices.
Whereas in the complete graph and coupon collecting problems we 
visited a (possibly) new vertex in one step,
a random walk on the $n$-star visits a (possibly) new vertex
in two steps: one step to each leaf and one step back.
We apply our approach to the complete graph and conclude that

@@

To solve the telescoping equations, observe that the walk is symmetric:
we could flip the walk over the vertical axis without changing $e_i$.
This makes sense because our intuition tells us that the only 
identifying feature of $i$ is its respective distances to the endpoints.
The logical conclusion is that $e_i=e_{N-i}$.
In particular, we have already seen that $e_0=e_N=0$ and it
naturally follows that $e_1=e_{N-1}$.
We use these observations to find $e_1$:

@@

\cref{thm:line} follows from \cref{eq:line} and the observation that any
line graph with $N+1$ vertices can be relabeled so that the left endpoint
is at $0$ and the right endpoint is at $N$.

@@

We write
\begin{align}
\E_0[T_N] &= \E_0[T_1] + \E_1[T_2] + \cdots + \E_{i}[T_{i+1}] + \cdots + \E_{N-1}[T_N]. \nonumber
\end{align}
where $\E_{i}[T_{i+1}]$ is the expected time from state $i$ to $i+1$.
Since there is only one edge incident to 0, we always move from 0 to 1.
From state $i\neq0$, we take one step in each direction with equal probability.
In half the cases, we have arrived at $i+1$.
In the other half of cases, we are in $i-1$.
It will take us $\E_{i-1}[T_i]$ steps back to $i$ and then another
$\E_i[T_{i+1}]$ steps to $i+1$.
Formally,
\begin{align}
\E_{i}[T_{i+1}] &= 1 + \frac{1}{2}(\E_{i-1}[T_i]+\E_i[T_{i+1}]) +\frac{1}{2}0 \nonumber \\
 &= 2 + \E_{i-1}[T_{i}]. \nonumber
\end{align}

@@

\subsection{Commute Time Identity} \label{sec:commute}
The commute time between vertices $a$ and $b$ is the expected 
number of steps for a random walk starting in $a$ to visit $b$
and then return to $a$.
Following \cite{DS84}, we use the electrical network analysis in \cref{sec:electric} to 
prove the commute time identity so we may use it to help us bound
cover times.

@@

Our goal is to bound the cover time in terms of the hitting time.
Consider the first term of the sum.
Recall that the hitting time $\hit$ is the maximum
expected time from any vertex to any other.
It follows that for any choice of $\sigma_1$,
the expected time from $n$ to $\sigma_1$ is less than or equal to $\hit$.
Formally, for $s$ an arbitrary state such that $1\leq s \leq n-1$,
$\E_n[T_1] = \E_n[T_s] \leq \hit$.

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[scale = 2]
	    \tikzstyle{vertex}=[draw, circle,fill=black, scale=.7]
	    \tikzstyle{edge}=[draw,line width = .5pt,-,black!100]
	    \node[vertex] (0) at (0,3) {};
	    \node[vertex] (1) at (1,2) {};
	    \node[vertex] (2) at (-1,2) {};
	    \node[vertex] (3) at (1.5,1) {};
	    \node[vertex] (4) at (.5,1) {};
	    \node[vertex] (5) at (-.5,1) {};
	    \node[vertex] (6) at (-1.5,1) {};
	    \node[vertex] (7) at (1.75,0) {};
	    \node[vertex] (8) at (1.25,0) {};
	    \node[vertex] (9) at (.75,0) {};
	    \node[vertex] (10) at (.25,0) {};
	    \node[vertex] (11) at (-.25,0) {};
	    \node[vertex] (12) at (-.75,0) {};
	    \node[vertex] (13) at (-1.25,0) {};
	    \node[vertex] (14) at (-1.75,0) {};
	    \draw[edge] (1) -- (0);
	    \draw[edge] (2) -- (0);
	    \draw[edge] (1) -- (3);
	    \draw[edge] (4) -- (1);
	    \draw[edge] (2) -- (5);
	    \draw[edge] (6) -- (2);
	    \draw[edge] (3) -- (7);
	    \draw[edge] (3) -- (8);
	    \draw[edge] (4) -- (9);
	    \draw[edge] (4) -- (10);
	    \draw[edge] (5) -- (11);
	    \draw[edge] (5) -- (12);
	    \draw[edge] (6) -- (13);
	    \draw[edge] (6) -- (14);
	\end{tikzpicture}
	\caption{A binary tree with $k=3$ has $n=15$.}\label{fig:binary}
\end{figure}

Following \cite{LP17},
consider an unweighted, balanced binary tree as in \cref{fig:binary}
with a single root $\rho$ and $k$ levels.
A vertex has two children if it is distance less than $k$
from the root and no children if it is a leaf at distance $k$ from the root.
There are $n = 1 + 2 + 4 + \cdots + 2^k = 2^{k+1} - 1$ vertices.

By \cref{eqn:commute}, the commute time between the root and a leaf $a$ is
\begin{align}
C R_{\rho, a} = 2 (n-1) k \nonumber.
\end{align}
Note that resistance adds in series so 
effective resistance is just the sum of the resistances along a path.
Then $\Rxy = i$ where $i$
is the length of the unique path between $x$ and $y$.

@@

\subsection{Spanning Tree Argument}\label{sec:spanning}
Following \cite{AF14}, 
we introduce the concept of a spanning tree to create
another upper bound for the cover time of a random walk.

@@

A tree is a connected graph with no cycles (i.e. there is exactly one path
between every pair of points.)
A spanning tree $\T$ for a connected graph $G$ is a tree with $V(\T) = V(G)$
and $E(\T) \leq E(G)$.
\cref{fig:span} shows an example spanning tree
where the bold edges indicate the edges in $E(\T)$
and the light edges indicate the edges in $E(G)$ but not $E(\T)$.
A consequence of the definition is that 
$|E(\T)| = n-1$.

@@

We compute the variance of $N_n$ by finding $\E[N_n^2]$ and $\E[N_n]^2$.
Let $\I_m$ be the indicator random variable for event $A_m$.
That is, $\I_m = 1$ if vertex $m$ is unvisited 0 otherwise.
We first find $\E[N_n^2]$
\begin{align}
\E[N_n^2] &= \E \left[ \left(\sum_{m=1}^n \I_m \right) ^2 \right] =
\E \left[ \sum_{m=1}^n \sum_{k=1}^n \I_m \I_k \right] =
\sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m). \nonumber
\end{align}
The second equality holds because we distribute terms.
The third equality holds because $\I_m \I_k = \I_{m \cap k}$
and the expectation of an indicator random variable is the event's probability.
Then we find $\E[N_n]^2$
\begin{align}
\E[N_n]^2 &= \E \left[ \left(\sum_{m=1}^n \I_m \right)
\left( \sum_{k=1}^n \I_k \right) \right] =
\sum_{1 \leq k, m \leq n} \pr(A_k) \pr(A_m).
\nonumber
\end{align}

Putting both together, we find the variance
\begin{align}
\Var[N_n] &= \E[N_n^2] - \E[N_n]^2 \nonumber \\
&= \sum_{1 \leq k, m \leq n} \pr(A_k \cap A_m) - P(A_k)P(A_m) \nonumber \\
&= n(n-1) \left[ \pr(A_k \cap A_m) - P(A_k)P(A_m) \right] + 
n \left[ \pr(A_k \cap A_m) - P(A_k)P(A_m) \right] \nonumber \\
&= n(n-1) \left[ (1-2/n)^r - (1-1/n)^{2r} \right] + 
n \left[ (1-1/n)^r  - (1-1/n)^{2r} \right]. \nonumber
\end{align}
where $k\neq m$ in the first term and $k=m$ in the second.

@@

Thus we conclude that $N_n/n$ converges in probability to $e^{-c}$.

The Poisson approximation of the binomial implies that if $n \rightarrow \infty$
and $r/n \rightarrow c$, then the number of visits to each vertex will approach
a Poisson distribution with mean $c$.
We can use this to intuite our latest result: the proportion of unvisited vertices
approaches $e^{-c}$.

@@

\begin{proof}
Observe that the chance a particular set of $k$ vertices are unvisited is
\begin{align}
(1-k/n)^r \nonumber.
\end{align}

@@

If we consider the location of the $m$ unvisited vertices,
and multiply probability that those $m$ vertices are unvisited
and the rest are visited,
\begin{align}
p_m(r,n) = {n \choose m} \left(1-\frac{m}{n}\right)^r p_0(r, n-m). \nonumber
\end{align}

@@

We now turn to the more tricky lower bound.
Notice that ${n \choose m} \geq (n-m)^m / m!$
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r
&\geq \left(1-\frac{m}{n}\right)^r \frac{(n-m)^m}{m!}
\left( \frac{n^m}{n^m} \right) \nonumber\\
&\geq n^m \left(1 - \frac{m}{n}\right)^r \left(1- \frac{m}{n}\right)^m
\frac{1}{m!}. \nonumber
\end{align}

As $n \rightarrow \infty$, $\left(1-\frac{m}{n}\right)^m \rightarrow 1$
and $1/m!$ is constant.
We use the Taylor series to bound the rest.
(The following equality is valid for $-1 \leq t \leq 1$
but we only need $0 \leq t \leq 1$ because $m/n \rightarrow 0$
and $m,n$ are counts of vertices with $m\leq n$.)
We apply
\begin{align}
\log(1-t) &= 0 - t - t^2/2 -t^3/3 - \cdots \nonumber\\
&\geq -t -t^2/2(1 + 1/2 + 1/4 + \cdots) = -t - t^2 \nonumber
\end{align}
to
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&= m \log n + r \log\left(1-\frac{m}{n}\right) \nonumber \\
& \geq m \log n - r\frac{m}{n} - r\left(\frac{m}{n}\right)^2. \nonumber
\end{align}

We use our assumption that $ne^{-r/n} \rightarrow \lambda$
to solve for $r$
\begin{align}
ne^{-r/n} &\rightarrow \lambda \nonumber\\
\log n - \frac{r}{n} &\rightarrow \log \lambda \nonumber\\
\frac{(n\log n - n\log\lambda) - r}{n} &\rightarrow 0 \nonumber
\end{align}
then
\begin{align}
r = (n\log n - n \log \lambda) + o(n) \nonumber.
\end{align}
%\begin{align}
%e^{\log n + -r/n} &\rightarrow e^{\log \lambda} \nonumber\\
%\log n + -r/n &= \log \lambda + o(n) \nonumber \\
%r &= n \log n - n \log \lambda +  o(n)n. \nonumber
%\end{align}
Since $r (m/n)^2 \rightarrow 0$ and
\begin{align}
\frac{rm}{n} &=m \log n - m \log \lambda +  o(n)m \nonumber \\
 m \log n - \frac{rm}{n}&\rightarrow m \log \lambda \nonumber
\end{align}
we have
\begin{align}
\log \left(n^m\left(1-\frac{m}{n}\right)^r \right)
&\geq m \log n - \frac{rm}{n} - \frac{rm}{n^2} \rightarrow \log \lambda^m. \nonumber
\end{align}
It follows that
\begin{align}
\lim_{n\rightarrow \infty} n^m\left(1-\frac{m}{n}\right)^r
&\geq \lambda^m. \nonumber
\end{align}
